My Cool Title

### 2019-04-29 paper.tex
Final commit before branching off. Also splitting all sentences into their own lines

\author{Jacobus C. Lock\inst{1} \and
  Gzegorz Cielniak\inst{1} \and
  Andrea Tramontano\inst{2} \and
  Nicola Bellotto\inst{1}
}
\authorrunning{J.C. Lock et. al.}
\institute{University of Lincoln, Lincoln, UK \and
  Universita Degli Studi Di Padova, Italy
}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.38\textwidth]{figures/system_use.png}
  \caption{The system in use during an experiment. }\label{fig:system-in-use}
\end{figure}

>>>>

\author{Jacobus C. Lock\inst{1} \and
  Grzegorz Cielniak\inst{1} \and
  Andrea Tramontano\inst{2} \and
  Nicola Bellotto\inst{1}
}
\authorrunning{J.C. Lock et. al.}
\institute{University of Lincoln, Lincoln, UK \and
  Universita Degli Studi Di Padova, Italy
}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/system_use.png}
  \caption{The system in use during an experiment. }\label{fig:system-in-use}
\end{figure}

Our active search system uses the camera's current and previous views as input and leverages its understanding of inter-object spatial relationships to determine the best navigation action to determine the best action to take to reach the target object.
To enable this, we implemented a partially observable Markov Decision Process (POMDP)~\cite{bellman1957markovian} on a mobile phone generates real-time navigation instructions to guide the user to their target object.
